Mahotas: Open source software for scriptable computer vision

### 2013-04-24 paper.tex
TXT Fix repetitions. Link to docs

Mahotas is released under a liberal open source license (MIT License) and is
available from \url{http://github.com/luispedro/mahotas} and from the Python Package
Index (\url{http://pypi.python.org/pypi/mahotas}).

@@

Version 1.0 of mahotas has been released recently and this is now a mature,
well-tested package (the first versions were made available over 4~years ago,
although the package was not named mahotas then). \footnote{Note for reviewers:
the version currently available (0.9.6) implements all functionality described
in this manuscript. I will release it as version 1.0 when this manuscript is
accepted to coincide with publication. Naturally, any bugs that are found and
reported in the meanwhile will be addressed.} Mahotas runs and is used on
different versions of Unix (including Linux, SunOS, and FreeBSD), Mac OS X, and
Windows.

@@

@@

\textbf{Additional system requirements}\\
None at runtime. Compilation from source requires a \cpp{} compiler.

\textbf{Dependencies}\\
At runtime, mahotas requires numpy to be present and installed. If compiling
from source, the Python headers and a \cpp{} compiler is required.

>>>>

Mahotas is released under a liberal open source license (MIT License) and is
available from \url{http://github.com/luispedro/mahotas} and from the Python Package
Index (\url{http://pypi.python.org/pypi/mahotas}). Tutorials and full API
documentation is available online at \url{http://mahotas.readthedocs.org/}.

@@

Version 1.0 of mahotas has been released recently and this is now a mature,
well-tested package (the first versions were made available over 4~years ago,
although the package was not named mahotas then). Mahotas runs and is used on
different versions of Unix (including Linux, SunOS, and FreeBSD), Mac OS X, and
Windows.

@@

There are binary packages available for Windows, maintained by Christoph
Gohlke, and for FreeBSD and Linux Frugalware through their respective package
systems.

@@

\textbf{Additional system requirements}\\
None at runtime. Compilation from source requires a \cpp{} compiler and the
Python development headers.

\textbf{Dependencies}\\
At runtime, mahotas requires numpy to be present and installed.
